%-------------------------
% Resume in Latex
% Author : Clinton Lunn
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\huge \scshape Clinton Lunn} \\ \vspace{1pt}
    \small 813-784-8758 $|$ \href{mailto:clinton@clintonlunn.com}{\underline{clinton@clintonlunn.com}} $|$ 
    \href{https://linkedin.com/in/clintonlunn}{\underline{linkedin.com/in/clintonlunn}} $|$
    \href{https://github.com/clintonlunn}{\underline{github.com/clintonlunn}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Florida State University}{Tallahassee, FL}
      {Master of Science in Geographic Information Sciences}{December 2017}
      
    \resumeSubheading
      {Florida State University}{Tallahassee, FL}
      {Bachelor of Science in Environmental Studies}{December 2013}

  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Availity}{Jacksonville, FL}
      {Software Engineer II}{March 2022 - Present}
    \resumeItemListStart
        \resumeItem{Led the migration from legacy Angular 1.x UIs to modern React.js and TypeScript platforms, optimizing user interfaces and improving overall experience.}
        \resumeItem{Designed and deployed responsive forms and filters for healthcare applications using Formik and Yup, streamlining user interactions and data validation processes.}
        \resumeItem{Incorporated Cucumber automation alongside Jest and React Testing Library, enhancing application testing and reliability.}
        \resumeItem{Routinely utilized tools including Selenium Webdriver, Postman, Splunk, and Testrail for comprehensive application monitoring, testing, and debugging.}
        \resumeItem{Engaged in troubleshooting and logic modifications within existing Java code, demonstrating adaptability and problem-solving capabilities in unfamiliar domains.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Availity}{Jacksonville, FL}
      {Software Engineer I}{August 2019 - February 2022}
    \resumeItemListStart
        \resumeItem{Participated in full-stack application development, enhancing features within an agile team environment.}
        \resumeItem{Automated data transformation and restructuring within HL7 documents using Mirth Connect, streamlining healthcare data processes.}
        \resumeItem{Aided in migrating parts of legacy Angular 1.x UIs to modern architectures, ensuring compatibility and performance.}
        \resumeItem{Collaborated with the team in troubleshooting, refining, and optimizing healthcare application components.}
    \resumeItemListEnd
    
    \resumeSubheading
      {UrbanSDK}{Jacksonville, FL}
      {GIS Consultant}{May 2022 - August 2023}
      \resumeItemListStart
        \resumeItem{Designed and executed transit-focused dashboards via ArcGIS Dashboards to support governmental initiatives.}
        \resumeItem{Integrated multiple dashboards on a singular platform using ArcGIS Enterprise Sites for streamlined access.}
        \resumeItem{Employed Tools: ArcGIS Online, ArcGIS Dashboards, ArcGIS Enterprise Sites.}
      \resumeItemListEnd

    \resumeSubheading
      {GIS Researcher and Developer}{January 2018 -- December 2022}
      {Florida Resources \& Environmental Analysis Center}{Tallahassee, FL}
      \resumeItemListStart
        \resumeItem{Maintained front-end web-mapping applications used by public and private entities across Florida.}
        \resumeItem{Developed custom data-driven mapping applications with advanced query capabilities and intuitive UI.}
        \resumeItem{Leveraged technologies and libraries including HTML, JavaScript, CSS, jQuery, SQL, Dojo, ArcGIS JavaScript API, ESRI Calcite, Leaflet, Bootstrap, and Git Version Control.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Web Development Consultant}{September 2021 -- December 2021}
      {Skin PS Brands}{}
      \resumeItemListStart
        \resumeItem{Consulted with customer service to resolve issues with internal ticketing software.}
        \resumeItem{Updated WordPress and Shopify websites per client requirements.}
        \resumeItem{Utilized technologies like Shopify, WordPress, and Gorgias.}
      \resumeItemListEnd

    \resumeSubheading
      {GIS Conflation Analyst (Temporary Contractor)}{April 2019 -- August 2019}
      {CSX}{Jacksonville, FL}
      \resumeItemListStart
        \resumeItem{Enabled effective coordination of project updates and workflow improvements across departments.}
        \resumeItem{Tested and validated railway data accuracy using internal GIS conflation tools.}
        \resumeItem{Communicated with field employees to verify imprecise data using technologies like ArcMap 10.X and proprietary web mapping plugins.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2017 -- December 2017}
      {Florida State University - Geography}{Tallahassee, FL}
      \resumeItemListStart
        \resumeItem{Guided and mentored students in an introductory GIS course.}
        \resumeItem{Assisted students with data acquisition and map-building using QGIS.}
        \resumeItem{Helped the lead instructor in evaluating assignments and inputting grades into the Blackboard student portal.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Technologies}{: HTML, JavaScript, CSS, jQuery, SQL, Dojo, ArcGIS JavaScript API, ESRI Calcite, Leaflet, Bootstrap, Git Version Control, QGIS, ArcMap 10.X, Shopify, WordPress, Gorgias}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

